Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-26 paper.tex
Revert float placement forcing Here
This reverts part of commit b9bdbc4f.
Update theta_distrib figures for HMNS test

% packages
\usepackage{amssymb}              % for \gtrsim ...
\usepackage{amsmath}              % for \text, align, split ...
\usepackage{color}                % for colorful margin notes
\usepackage[mathscr]{euscript}    % for \mathscr
\usepackage{float}                % for better control of figure placement
\usepackage{graphicx}             % for \includegraphics
\usepackage{hyperref}             % for \url and \href
\usepackage{listings}             % for typesetting code with \lstinline
\usepackage{tabularx}             % for tabularx

@@

% force all figures to be placed right where they are in the text
\floatplacement{figure}{H}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-luminosity_R}
  % Data:   $DIR/PositionDistributions
  % Data gathered using: $DIR/CollectPositionDistributions.sh
  % Script: $DIR/GnuScripts/plot-theta_distributions-R-fixed_r.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03
  \caption{Radial number fluxes, $K_r$, as functions of colatitude $\theta$.
    Sampled for observers at fixed coordinate distances from the center
    of the star, with $r=250\,{\rm km}$.
    Here radial fluxes are multiplied by the portion of solid angle
    represented by each observer, so that the total luminosity is
    computed by summing all the points.}
  \label{fig:nsns_theta_distrib_R}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-luminosity_L}
  % see notes from theta_distrib-250km-luminosity_R
  % Script: $DIR/GnuScripts/plot-theta_distributions-L-fixed_r.gnu
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_R} but radial energy
    fluxes, $H_r$.}
  \label{fig:nsns_theta_distrib_L}
\end{figure}

The distributions of radial fluxes over observer position are shown
in Figs.~\ref{fig:nsns_theta_distrib_R} and \ref{fig:nsns_theta_distrib_L}.
With the \emph{noscat} treatment the $\nu_x$ luminosities are relatively
constant in $\theta$, because the disk is optically thin to $\nu_x$,
and most of the neutrinos come from the hypermassive neutron star,
which is roughly spherical.
The slight upward trend in $\nu_x$ luminosities with $\theta$ may be due to
asymmetries in the configuration.
It is not due to the Doppler shift from the rapid rotation of the star
(a hypothesis we tested by setting $u_i=0$ and $W=1$ in the ray
tracing equations).
Because of their larger absorption cross section,
the disk is not optically thin to $\nu_e$ and $\bar{\nu}_e$,
and observers within view of the hot hypermassive neutron star measure
the largest radial fluxes.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-avg_eps}
  % see notes from theta_distrib-250km-luminosity_R
  % Script: $DIR/GnuScripts/plot-theta_distributions-avg_eps-fixed_r.gnu
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_R} but
    average energies $\langle \varepsilon \rangle = J/G$.}
  \label{fig:nsns_theta_distrib_avg_eps}
\end{figure}

>>>>

% packages
\usepackage{amssymb}              % for \gtrsim ...
\usepackage{amsmath}              % for \text, align, split ...
\usepackage{color}                % for colorful margin notes
\usepackage[mathscr]{euscript}    % for \mathscr
\usepackage{graphicx}             % for \includegraphics
\usepackage{hyperref}             % for \url and \href
\usepackage{listings}             % for typesetting code with \lstinline
\usepackage{tabularx}             % for tabularx

@@

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-Kr}
  % Data_a:   $DIR/PositionDistributions/*Lev1-e30a120b20-01*
  % Data_s:   $DIR/PositionDistributions/*Lev1-e30a60b10-01*
  % Data gathered using: $DIR/CollectPositionDistributions.sh
  % Script: $DIR/GnuScripts/plot-theta_distributions-Hr-fixed_r.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03
  \caption{Radial number fluxes, $K^r(\theta)$,
    as defined in Eqn.~\ref{eqn:Kr_minkowski},
    in the hypermassive neutron star configuration.
    Sampled for observers at fixed coordinate distances from the center
    of the star, with $r=250\,{\rm km}$.
  }
  \label{fig:nsns_theta_distrib_Kr}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-Hr}
  % see notes from theta_distrib-250km-Kr
  % Script: $DIR/GnuScripts/plot-theta_distributions-Hr-fixed_r.gnu
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_Kr} but radial energy
    fluxes $H^r(\theta)$ as defined in Eqn.~\ref{eqn:Hr_minkowski}.
  }
  \label{fig:nsns_theta_distrib_Hr}
\end{figure}

The distributions of radial fluxes over observer position are shown
in Figs.~\ref{fig:nsns_theta_distrib_Kr} and \ref{fig:nsns_theta_distrib_Hr}.
With the \emph{noscat} treatment the $\nu_x$ luminosities are relatively
constant in $\theta$, because the disk is optically thin to $\nu_x$,
and most of the neutrinos come from the hypermassive neutron star,
which is roughly spherical.
The slight upward trend in $\nu_x$ luminosities with $\theta$ may be due to
asymmetries in the configuration.
It is not due to the Doppler shift from the rapid rotation of the star
(a hypothesis we tested by setting $u_i=0$ and $W=1$ in the ray
tracing equations).
Because of their larger absorption cross section,
the disk is not optically thin to $\nu_e$ and $\bar{\nu}_e$,
and observers within view of the hot hypermassive neutron star measure
the largest radial fluxes.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-avg_eps}
  % see notes from theta_distrib-250km-Kr
  % Script: $DIR/GnuScripts/plot-theta_distributions-avg_eps_from_fluxes-fixed_r.gnu
  \caption{Same as Fig.~\ref{fig:nsns_theta_distrib_Kr} but
    average energies of radial fluxes
    $\langle\tilde{\varepsilon}\rangle(\theta)=H^r(\theta)/K^r(\theta)$,
    as defined in Eqns.~\ref{eqn:Kr_minkowski} and \ref{eqn:Hr_minkowski}.
  }
  \label{fig:nsns_theta_distrib_avg_eps}
\end{figure}
